---
title: " "
output:
  html_document:
    includes:
      in_header: GA_Script.html
---
```{r setup, include=FALSE} 
library(rentrez)  # For fetching PubMed articles
library(DT)       # For interactive tables
library(dplyr)    # For data manipulation
library(httr) 
library(jsonlite)
library(rentrez)
library(reshape)
library(ggplot2)
library(knitr)
library(lubridate)

```

# KHS Research 

Kidney Health Services at Metro North conducts research aimed at improving patient care and outcomes in kidney health. Our researchers includes professionals from nursing, dietetics, pharmacy, and medical fields, collaborating to address the complex needs of patients with chronic kidney disease and other renal conditions.

We engage in clinical trials as well as undertake basic science based research, ranging from cutting-edge omics technologies to investigate novel therapies and interventions. Our approach emphasizes networked and collaborative strategies, integrating expertise from various disciplines to enhance our understanding of kidney health and disease. This collaborative effort aims to translate research findings into practical applications for patient care.

Reach out if you would like to collaborate or join a research project. 


```{r, echo=F,eval=F,message=FALSE, warning=FALSE}


# Create a dataframe with researcher information
researchers <- data.frame(
  Name = c("Eoin O'Sullivan", "Monica Ng", "Saw Yu Mon", "Dharmenaan Palamuthusingam","Helen Healy","Shaun Chandler","George John","Martin Wooley","Sharad Ratanjee","Dwarakanathan Ranganathan","Kirsten Hepburn","Brian Doucet","Prianka Puri","Madhivanan Sundaram"),
  
  ORCID = c("0000-0002-7709-6595", "0000-0002-0431-9110", "tbc", "0000-0003-1505-3482","0000-0003-4342-5300","0000-0002-6294-0060","0000-0001-6145-1591","0000-0002-7870-5073","0000-0002-6024-7684","0000-0003-1215-1773","0000-0003-3142-9195","0000-0003-1656-2385","0000-0003-0752-4651","0000-0002-7331-441X"),
  
  Website = c("https://scholar.google.com.au/citations?hl=en&pli=1&user=mKQFjGsAAAAJ", "https://scholar.google.co.uk/citations?hl=en&user=kznyXfMAAAAJ", "https://www.healthhubdoctorsmorayfield.com.au/dr-sarah-mon/", "https://www.researchgate.net/profile/Dharmenaan-Palamuthusingam","https://cre-ckd.centre.uq.edu.au/profile/47/helen-healy","https://orcid.org/0000-0002-6294-0060","https://www.researchgate.net/profile/George-John-11","https://www.webofscience.com/wos/author/record/P-1554-2015","https://www.researchgate.net/profile/Sharad-Ratanjee","https://www.researchgate.net/profile/Dwarakanathan-Ranganathan","https://orcid.org/0000-0003-3142-9195","https://www.researchgate.net/profile/Brian-Doucet-3","https://www.researchgate.net/profile/Prianka-Puri","https://www.researchgate.net/profile/Madhivanan-Sundaram")
  
)

# Arrange the dataframe alphabetically by Name
researchers <- researchers %>%
  arrange(Name)

# Modify the ORCID column to include valid ORCID URLs with anchor tags
researchers$ORCID <- paste0("<a href='https://orcid.org/", researchers$ORCID, "'>", researchers$ORCID, "</a>")

# Modify the Website column to display "link" with a clickable URL
researchers$Website <- paste0("<a href='", researchers$Website, "'>link</a>")

# Generate the table in HTML format
kable(researchers, format = "html", escape = FALSE, table.attr = "style='width:100%;'", align = "l")
  
```

# KHS Output Overview


```{r, echo=FALSE}
searchstring<-"(Kidney Health Service[Affiliation]) OR (Eoin O'Sullivan) OR (Eoin Daniel O'Sullivan) OR (0000-0002-7709-6595) OR (Monica Ng) OR (0000-0002-0431-9110) OR (Palamuthusingam D) OR (0000-0003-1505-3482) OR (Mon SY) OR (Dwarakanathan Ranganathan) OR (0000-0002-7709-6595) OR (0000-0002-0431-9110) OR (0000-0003-1505-3482) OR (0000-0003-4342-5300) OR (0000-0003-1215-1773) or (0000-0002-6294-0060) or (0000-0003-4342-5300)or (0000-0002-6294-0060) or (0000-0001-6145-1591) or (0000-0002-7870-5073) or (0000-0002-6024-7684) or (0000-0003-1215-1773) or (0000-0003-3142-9195) or (0000-0003-1656-2385) or (0000-0003-0752-4651)"

search <- entrez_search(db = "pubmed",
                              term = searchstring, retmax=5000,use_post=TRUE,web_history =T)
multi_summs <- entrez_summary(db="pubmed", id=search$ids)
library(ggplot2)
search_year <- function(year, term){
    query <- paste(term, "AND (", year, "[PDAT])")
    entrez_search(db="pubmed", term=query, retmax=0)$count
}

year <- 2008:2025
papers <- sapply(year, search_year, term= searchstring, USE.NAMES=FALSE)

data <- data.frame(year, papers)

# Create the ggplot
ggplot(data, aes(x = year, y = papers)) +
    geom_line() +                      
    geom_point() +
    ggtitle("KHS Research Output - by KHS affiliation & affiliated Researcher output") +   
    xlab("Year") +                     
    ylab("Number of Papers") +         
    theme_bw()                        

```

# KHS top Journals

The data above is tabulated and the top 20 journals by frequency of publication are presented below.


```{r, echo=FALSE,eval=T}


journals <- extract_from_esummary(multi_summs, "source")
journal_freq <- as.data.frame(table(journals, dnn="journal"), responseName="n.papers")

top_journals <- head(journal_freq[order(-journal_freq$n.papers), ], 20)
ggplot(top_journals, aes(reorder(journal, n.papers), n.papers)) + 
    geom_point(size=4) + 
    coord_flip() + 
   ylab("Number of papers") +
 scale_y_continuous(breaks = 1:20,minor_breaks = NULL)+
    scale_x_discrete("Journal") +
    theme_minimal() +
    ggtitle("Top 20 Most Frequent Journals, 2008-2025") 

```


Methodology: These data are generated in R using a call to the Entrez-pubmed database through the R package "rentrez" - well the excellent fork by [Allen Baron](https://github.com/allenbaron) that overcomes a search string length limitation. The search term used is a manually updated list of staff names and ORCID IDs, as well as variations on the string "Kidney Health Service[Affiliation]". This isn't an exact (or high yield) process and as such it is likely to be a tad incomplete as well as having a non-zero false positive rate, but for the purposes of graphing trends in output its fairly effective.  

